SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-27 quiz.tex
Finish question templates. Add screenshot.

\iffalse
\author{\IEEEauthorblockN{Konrad Höffner}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-7358-3217}}
\and
\IEEEauthorblockN{Franziska Jahn}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0002-7687-8544}}
\and
\and
\IEEEauthorblockN{Alfred Winter}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
%alfred.winter@imise.uni-leipzig.de}
\url{https://orcid.org/0000-0003-0179-954X}}
\and
\IEEEauthorblockN{Thomas Pause}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-5832-4890}}
}
\fi
\begin{abstract}
%Textbooks contain abstract knowledge about a domain.
%Textbooks about information management in hospitals describe the planning, monitoring and directing of a hospital's information system.
SNIK is a knowledge base about the management of health information systems generated by extracting Linked Data from textbooks and other sources.
%SNIK consists of the manually transformed content of three textbooks as Linked Open Data.
SNIK Quiz demonstrates 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
%The data model describes information management functions, roles executing these functions and the information used or updated by these functions.

@@

\section{Introduction}
%A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
%This includes its different application systems, computers, and network components as well as their users.
Medical informatics students, who are trained for executive positions in information management (IM) departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from three textbooks~\citep{bb,ob,he} and other sources such as interviews in the form of Linked Open Data.
SNIK describes health information management (HIM) functions, roles executing these functions, and entity types, the information used or updated by these functions, see \cref{fig:metamodel}.
%Because the textbooks describe those concepts in the abstract sense, and not those of any concrete hospital, those entities are modelled as classes and individuals at the same time, using OWL 2 DL punning.
%Thus, \emph{function}, \emph{role} and \emph{entity type} are metaclasses and the ontology of SNIK is a meta model as depicted in \cref{fig:metamodel}.
SNIK version \snikversionlink{} contains \sniktriples{} triples describing \snikproperties{} properties and \snikclasses{} classes, of which there are \snikroles{} roles, \snikfunctions{} functions and \snikentitytypes{} entity types.
%Applications include a graph visualization for exploratiory learning, 
This paper presents SNIK Quiz, a browser game in which a student answers multiple-choice questions about HIM including an evaluation by domain experts and a student.

%A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing those activities.
%Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
%There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
%Three textbooks provide different views on the domain of Hospital Information Management:
%\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
%\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
%The focus of tactical management lies on the planning and operation of projects.
%\citet{he} explains information management beyond the scope of healthcare.
%Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}
%
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
%We conclude with plans for future work on interlinking and visualization.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
%Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
%These are only implicitly known or not known at all by experts in the field.
%
%
%Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

@@

\section{Methods}
\begin{figure*}
\caption{The SNIK meta model}
\label{fig:metamodel}
\centering
\includegraphics[width=\textwidth,trim={0 0 0 135mm},clip]{img/metamodel9s.pdf}
\end{figure*}
SNIK Quiz is designed as single-player game for English speaking students of Medical Informatics.
This group is diverse and includes students of Medicine, who may not have a background in Computer Science and Semantic Web technologies.
Target devices are PCs, tablets and smartphones, so multiple operating systems and input methods need to be supported.
Thus, SNIK Quiz is designed as an multiple choice quiz with at most four possible answers and published as an open source\footnote{\url{https://github.com/snikproject/snik-quiz}} web application.

@@

\begin{table}[t]
\caption{Quiz question templates with examples. When not otherwise noted, distractors are wrong answers that are neighbors of degree at most 2 of the correct answer.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Subject}		&Ask for the subject of a (subject, relation, object) triple given the relation and object.\\
%						&Distractors are labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object but which are connected to the correct answer with a path of length at most 2.\\
Stem					&\emph{Who is \emph{responsible for} \emph{Medical Admission}?}\\
Key						&\emph{Physician}\\
Distractors				&\emph{Surgeon}, \emph{Health Care Professional}, \emph{Senior Physician}\\
\midrule
\textbf{Object}			&Ask for the object of a (subject, relation, object) triple given the subject and relation.\\
Stem					&\emph{The \emph{Specification Team} is \emph{responsible for}}$\ldots$\\
Key						&\emph{Functional Specification Document}\\
Distractors: 			&\emph{Project Team Member}, \emph{Sponsor}, \emph{Defining Project Organization}\\
\midrule
\textbf{Definition}		&Ask for the class that fits the given textbook definition.\\
Stem					&\emph{What is defined by this?}\\
						&\enquote{X assures a defined quality of all processes and outcomes of the hospital}\\
Key						&\emph{Internal Quality Management}\\
Distractors				&\emph{Activity}, \emph{Complaint}, \emph{Diagnosis}\\
\midrule
\textbf{Intertwined}	&The correct answer is a triangle in the graph. The distractors are of different shapes based on the difficulty. See \cref{fig:intertwined}.\\
Stem					&In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Key						&\emph{Chief Information Officer -- Department of Information management -- IM Staff}\\
Distractor 1			&\emph{Chief Information Officer -- Strategic Gap -- Corporate Strategy}\\
Distractor 2			&\emph{Chief Information Officer -- Ticket Evaluation -- Project Monitoring}\\
\midrule
\textbf{Close-By}		&\\
Stem \\
Key \\
Distractors \\
\midrule
\textbf{Label-Definition}	&Present different definitions and ask, which of them fits the given entity.\\
Stem					&\emph{How is \enquote{Chief Executive Officer} defined?}\\
Key						&\emph{Responsible for setting and carrying out the strategic plans and policies of an enterprise.}\\
Distractors				&labels of entities within a path length of at most 2, e.g. \emph{Anyone who has direct or indirect influence on or interest in a component of an information system.}\\
\midrule
\textbf{Occurence}				& Asks where a term is set to exist in the used ontologies of SNIK. These ontologies are made up of relations based on the books \cite{ob} and \cite{bb}.\\
						&Stem:  In which contexts does the term \enquote{Health Insurance Company} occur? \\
Example:				&Key: Strategic Information Management \\
						&Distractor 1: Tactical Information Management \\
						&Distractor 2: Both Contexts \\
						&Distractor 3: Neither \\
\bottomrule
\end{tabulary}
\end{table}

@@

% TODO: reformulate now that its not future work anymore but part of the paper
An ongoing bachelor's thesis~\citep{snikquiz} is investigating different strategies of generating complex questions, answers and distrators.

@@

\begin{figure}
\includegraphics[width=0.7\textwidth]{img/intertwined_cml.png} 
\caption{Left to right: correct answer, difficult and easy distractor for the \emph{intertwined} question type.}
\label{fig:intertwined}
\end{figure}

@@

% transposed
\begin{table}[h]
\begin{tabularx}{\textwidth}{Xcccccc}
\toprule
			&label-definition	&definition	&contains	&intertwined	&closeMatch	&occurence\\
interview 1	&3					&4			&5--6		&7				&8			&7\\
interview 2	&4					&6			&7			&7--8			&7--8		&5\\
interview 3	&3					&3			&6			&8				&8			&7\\
\bottomrule
\end{tabularx}
\caption{Rating given by interviewees based on the complexity of the questions on a scale between 1 and 10 with 10 representing maximum complexity.}
\label{tabelle:eval_komplex}
\end{table}

>>>>

\iffalse
\author{\IEEEauthorblockN{Konrad Höffner}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-7358-3217}}
\and
\IEEEauthorblockN{Franziska Jahn}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0002-7687-8544}}
\and
\and
\IEEEauthorblockN{Alfred Winter}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
%alfred.winter@imise.uni-leipzig.de}
\url{https://orcid.org/0000-0003-0179-954X}}
\and
\IEEEauthorblockN{Thomas Pause}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-5832-4890}}
}
\fi
\begin{abstract}
%Textbooks contain abstract knowledge about a domain.
%Textbooks about information management in hospitals describe the planning, monitoring and directing of a hospital's information system.
SNIK is a knowledge base about the management of health information systems generated by extracting Linked Data from textbooks and other sources.
%SNIK consists of the manually transformed content of three textbooks as Linked Open Data.
We present SNIK Quiz, a browser game in which students answer multiple-choice questions about information management in hospitals based on SNIK.
The questions are semi-automatically generated using several question templates in order to train basic facts, more complex patterns, and connections between textbooks encoded in SNIK.
%The data model describes information management functions, roles executing these functions and the information used or updated by these functions.

@@

\section{Introduction}
%A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
%This includes its different application systems, computers, and network components as well as their users.
Medical informatics students, who are trained for executive positions in information management (IM) departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from three textbooks~\citep{bb,ob,he} and other sources such as interviews in the form of Linked Open Data.
SNIK describes health information management (HIM) functions, roles executing these functions, and entity types, the information used or updated by these functions, see \cref{fig:metamodel}.
%Because the textbooks describe those concepts in the abstract sense, and not those of any concrete hospital, those entities are modelled as classes and individuals at the same time, using OWL 2 DL punning.
%Thus, \emph{function}, \emph{role} and \emph{entity type} are metaclasses and the ontology of SNIK is a meta model as depicted in \cref{fig:metamodel}.
SNIK version \snikversionlink{} contains \sniktriples{} triples describing \snikproperties{} properties and \snikclasses{} classes, of which there are \snikroles{} roles, \snikfunctions{} functions and \snikentitytypes{} entity types.
%Applications include a graph visualization for exploratiory learning, 
%
\begin{figure}
\caption{The SNIK Quiz browser game available at \url{https://www.snik.eu/quiz}.}
\label{fig:snikquiz}
\centering
\includegraphics[width=0.6\textwidth]{img/snik-quiz.png}
\end{figure}
This paper presents SNIK Quiz, an open source\footnotemark{} browser game, see \cref{fig:snikquiz}, in which students answer multiple-choice questions about HIM, including an evaluation by domain experts and a student.
\footnotetext{Source code available under the MIT license at \url{https://github.com/snikproject/quiz}. The user interface is a fork of \url{https://github.com/davidrayoussef/react-quiz}.}
%A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing those activities.
%Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
%There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
%Three textbooks provide different views on the domain of Hospital Information Management:
%\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
%\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
%The focus of tactical management lies on the planning and operation of projects.
%\citet{he} explains information management beyond the scope of healthcare.
%Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}
%
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
%We conclude with plans for future work on interlinking and visualization.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
%Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
%These are only implicitly known or not known at all by experts in the field.
%
%
%Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

@@

\section{Methods}
\begin{figure*}
\caption{The SNIK meta model}
\label{fig:metamodel}
\centering
\includegraphics[width=\textwidth,trim={0 0 0 135mm},clip]{img/metamodel9s.pdf}
\end{figure*}
SNIK Quiz is designed as single-player game for English speaking students of Medical Informatics.
This group is diverse and includes students of Medicine, who may not have a background in Computer Science and Semantic Web technologies.
Target devices are PCs, tablets and smartphones, so multiple operating systems and input methods need to be supported.
Thus, SNIK Quiz is designed as an multiple choice quiz with at most four possible answers and published as an open source web application.

@@

\begin{table}[t]
\caption{Quiz question templates with examples. When not otherwise noted, distractors are wrong answers that are neighbors of degree at most 2 of the correct answer.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Subject}		&Ask for the subject of a (subject, relation, object) triple given the relation and object.\\
%						&Distractors are labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object but which are connected to the correct answer with a path of length at most 2.\\
Stem					&\emph{Who is responsible for Medical Admission?}\\
Key						&\emph{Physician}\\
Distractors				&\emph{Surgeon}, \emph{Health Care Professional}, \emph{Senior Physician}\\
\midrule
\textbf{Object}			&Ask for the object of a (subject, relation, object) triple given the subject and relation.\\
Stem					&\emph{The Specification Team is responsible for}$\ldots$\\
Key						&\emph{Functional Specification Document}\\
Distractors: 			&\emph{Project Team Member}, \emph{Sponsor}, \emph{Defining Project Organization}\\
\midrule
\textbf{Definition}		&Ask for the entity that fits the given textbook definition.\\
Stem					&\emph{What is defined by this? \enquote{X assures a defined quality of all processes and outcomes of the hospital}}\\
Key						&\emph{Internal Quality Management}\\
Distractors				&\emph{Activity}, \emph{Complaint}, \emph{Diagnosis}\\
\midrule
\textbf{Definitions}	&Present different definitions and ask, which of them fits the given entity.\\
Stem					&\emph{What defines the term Data Warehouse System?}\\
Key						&\emph{Application component that contains data which have been extracted from other application components, in order to support either hospital management or clinical research.}\\
Distractors				&\emph{Defines the hospital’s long-term strategic goals}\\
						&\emph{An application component where the controlling rules for data processing are implemented as executable software.}\\
						&\emph{Summarizes monitored key performance indicators (KPIs) and compares them to the expected future state}\\
\midrule
\textbf{Intertwined}	&The correct answer is a triangle in the graph. The distractors instead form different shapes based on the difficulty. See \cref{fig:intertwined}.\\
Stem					&In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Key						&\emph{Chief Information Officer -- Department of Information management -- IM Staff}\\
Distractor 1			&\emph{Chief Information Officer -- Strategic Gap -- Corporate Strategy}\\
Distractor 2			&\emph{Chief Information Officer -- Ticket Evaluation -- Project Monitoring}\\
\midrule
\textbf{Occurence}		&Asks where a term is set to exist in the used ontologies of SNIK. These ontologies are made up of relations based on the books \cite{ob} and \cite{bb}.\\
						&Stem:  In which contexts does the term \enquote{Health Insurance Company} occur? \\
Example:				&Key: Strategic Information Management \\
						&Distractor 1: Tactical Information Management \\
						&Distractor 2: Both Contexts \\
						&Distractor 3: Neither \\
\textbf{CloseMatch}		&Transfer knowledge about one textbook~\citep{bb} to the other~\citep{ob} by confirming or denying statements about entity pairs that are marked as near equivalent.\\
Stem					&\emph{In the Strategic Information Management, the Consultant is associated with the Long-Term HIS Planning, while in the Tactical Information Management, the Consultant is responsible for the Functional Specification Document.}\\
Key						&True\\
Distractor				&False\\
\bottomrule
\end{tabulary}
\end{table}

@@

@@

\begin{figure}
\includegraphics[width=0.7\textwidth]{img/intertwined_cml.png} 
\caption{Left to right: correct answer, difficult and easy distractor for the \emph{intertwined} question type~\citep{snikquizba}.}
\label{fig:intertwined}
\end{figure}

@@

% transposed
\begin{table}[h]
\begin{tabularx}{\textwidth}{Xcccccc}
\toprule
			&definitions		&definition	&subject	&intertwined	&closeMatch	&occurence\\
\midrule
interview 1	&3					&4			&5--6		&7				&8			&7\\
interview 2	&4					&6			&7			&7--8			&7--8		&5\\
interview 3	&3					&3			&6			&8				&8			&7\\
\bottomrule
\end{tabularx}
\caption{Rating given by interviewees based on the complexity of the questions on a scale between 1 and 10 with 10 representing maximum complexity~\citep{snikquizba}.}
\label{tabelle:eval_komplex}
\end{table}
